---
title: "Airbnb in London - How much to pay?"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float: true
    toc_depth: 2
    # css: style.css
  pdf_document:
    toc: yes
    toc_depth: '2'
bibliography: bibliography.bib
---

```{r include=FALSE}
library(ggplot2)
library(dplyr)
library(gridExtra)
library(rgdal)
# install.packages("broom")
load("data.RData")
data <- tbl_df(data)
```

# Introduction

Determinants of the Price

Assumption: Rating and Location have a major impact on the price of the Airbnb

How do the ratings work: https://www.airbnb.co.uk/help/article/1257/how-do-star-ratings-work

# Description of the dataset

## Initial dataset

Source: Inside Airbnb

Link to dataset:  http://data.insideairbnb.com/united-kingdom/england/london/2017-03-04/data/listings.csv.gz

London Map: https://github.com/Robinlovelace/Creating-maps-in-R

```{r results='hold'}
print(paste("Observations:",nrow(data)))
print(paste("Variables:",ncol(data)))
```

## Custom adjustments

<h3>Select: Variables of interest</h3>

General
last_scraped (date)
host_id
room_type (as categories)

Price


Number of Reviews
Review Rating

Location (latitude / longitude)

```{r}
data_short <- data %>% select(last_scraped, host_id, room_type, price, guests_included,
                              number_of_reviews, review_scores_rating,
                              latitude, longitude)
```

<h3>Filter: Observations of interest</h3>

Filter all Airbnbs that do not have a Rating (price and location always included)

```{r}
data_short <- data_short %>% filter(!is.na(review_scores_rating))
```

Filter only Private / Shared Rooms, no full Apartments

```{r}
data_short <- data_short %>% filter(grepl("room$", room_type))
```

<h3>Mutate: Price per Person and Distance</h3>

Price per Person

```{r}
data_short$price <- as.double(substr(paste(data_short$price), 2, 500))
data_short <- data_short %>% filter(!is.na(price))
data_short <- data_short %>% mutate(price_pp = price / guests_included)
data_short <- data_short %>% filter(!is.na(price_pp))

data_short <- data_short %>% filter(price_pp < 150)
```

Midpoint London Westminster -> Distance from midpoint by using 
Coordinates of Westminster (source Google)
latitude 51.5002
longitude -0.1332

$Dist=\sqrt{(lo_{West}-lo_{BnB})2+(la_{West}-la_{BnB})2}$

```{r}
data_short <- data_short %>% mutate(dist = sqrt((51.5002 - round(latitude, 4)) ^ 2 +
                                                  (-0.1332 - round(longitude, 4)) ^ 2))
```


<h4>Let´s take a look at our new dataset</h4>

```{r}
glimpse(data_short)
```

```{r results='hide'}
lnd <- readOGR(dsn = "map_data", layer = "london_sport")
lnd_f <- broom::tidy(lnd)
lnd$id <- row.names(lnd)
lnd_f <- left_join(lnd_f, lnd@data)
map <- ggplot(lnd_f, aes(long, lat, group = group, fill = Partic_Per)) + geom_polygon() + coord_equal()
```

```{r}
map
```


# Descriptive statistics

## Univariant descriptives

<h3>Groups within the data</h3>

```{r}
d1 <- data_short %>% group_by(room_type) %>% summarise(n = n())
g1 <- d1 %>% ggplot(aes(x = room_type, y = n)) + geom_bar(stat = "identity")

d2 <- data_short %>% group_by(number_of_reviews) %>% summarise(n = n())
g2 <- d2 %>% ggplot(aes(x = number_of_reviews, y = n)) + geom_bar(stat = "identity")

d3 <- data_short %>% group_by(host_id) %>% summarise(number_of_listings = n()) %>% group_by(number_of_listings) %>% summarise(n = n())
g3 <- d3 %>% ggplot(aes(x = number_of_listings, y = n)) + geom_bar(stat = "identity")

grid.arrange(g1, g2, g3, nrow = 3)
```

Result: Only Grouping by Room Type necessary

<h3>Summary for variables of interest</h3>

```{r results='hold'}
data_short %>% group_by(room_type) %>% summarise(min = min(price_pp),
                                                 q_25 = quantile(price_pp, .25),
                                                 median = median(price_pp),
                                                 q_75 = quantile(price_pp, .75),
                                                 max = max(price_pp))
data_short %>% ggplot(aes(room_type, price_pp)) + geom_boxplot() + coord_flip()
```
```{r results='hold'}
data_short %>% group_by(room_type) %>% summarise(min = min(review_scores_rating),
                                                 q_25 = quantile(review_scores_rating, .25),
                                                 median = median(review_scores_rating),
                                                 q_75 = quantile(review_scores_rating, .75),
                                                 max = max(review_scores_rating))
data_short %>% ggplot(aes(room_type, review_scores_rating)) + geom_boxplot() + coord_flip()
```
```{r results='hold'}
data_short %>% group_by(room_type) %>% summarise(min = min(dist),
                                                 q_25 = quantile(dist, .25),
                                                 median = median(dist),
                                                 q_75 = quantile(dist, .75),
                                                 max = max(dist))
data_short %>% ggplot(aes(room_type, dist)) + geom_boxplot() + coord_flip()
```

## Bivariant descriptives

```{r results='hold'}
data_short %>% ggplot(aes(x = review_scores_rating, y = price_pp)) + geom_point(aes(colour = factor(room_type)))
data_short %>% group_by(room_type) %>% summarise(cov = cov(review_scores_rating, price_pp), cor = cor(review_scores_rating, price_pp))
```

```{r results='hold'}
data_short %>% ggplot(aes(x = dist, y = price_pp)) + geom_point(aes(colour = factor(room_type)))
data_short %>% group_by(room_type) %>% summarise(cov = cov(dist, price_pp), cor = cor(dist, price_pp))
```

# Testing and Regression

# Conclusion

# References